Chasing \rainbows{} and ocean glint:\\ Inner working angle constraints for the Habitable Worlds Observatory

### 2023-05-03 src/tex/ms.tex

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/Phase_curves.pdf}
    \caption{The phase curves of the normalized polarized flux of a planet with a wavy ocean surface and an Earth-like atmosphere in an edge-on orbit (the planet thus exhibits phase angles ranging from 0$^\circ$ to 180$^\circ$ along its orbit). The wind speed over the ocean is 7~m/s. The clouds in the planet's atmosphere consist of spherical water droplets. The cloud coverage fraction is 0.5. The cloud pattern is patchy and the glint is kept cloud-free to maximize the glint signature \citep[see also Fig. 9 of][from which we took the mean signal of 300 planets with randomly generated patchy cloud patterns + 2 standard deviations, representative for cloud-free glint scenarios; the 'noise' at the larger phase angles and longer wavelengths is due to the variation in the location of cloud patches]{treesandstam2019}. The 
    polarized flux is normalized to the total (unpolarized + polarized) flux (it is thus in fact the degree of polarization). Note that the reference plane for the
    polarized flux is chosen such that only the polarized components perpendicular or parallel to the plane differ significantly from zero.
 %   and the latter
 %   is equals the planet's geometric albedo at phase angle $\alpha = 0^\circ$.
        %The cloudy scenario includes a low-altitude, Earth-like water 
        %cloud deck. 
        Below the plot, we show the phase angle ranges that cover the
        characteristic features of glories, rainbows, Rayleigh scattering, glint, and forward scattering by cloud particles (note that features partly overlap
        with each other).  
        %Throughout the paper we approximate feature sensitivity ranges as those that capture the rise and fall of peaks in polarized light for most habitable zone species in the UV, Optical, and IR (phase angles: glint $\sim\qtyrange{50}{70}{\degree}$; rainbow $\sim\SIrange{140}{160}{\degree}$; Rayleigh narrow of quadrature, and other forward and backscattering effects at the widest and narrowest phase angles).
    }
    \label{fig:bottplot}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics{figures/figure-1-bott-plot.pdf}
    \script{create-figure-1-bott-plot.py}
    \caption{
        The phase curves of the normalized polarized flux of a planet with a wavy ocean surface and an Earth-like atmosphere in an edge-on orbit (the planet thus exhibits phase angles ranging from \qty{0}{\degree} to \qty{180}{\degree} along its orbit). 
        The wind speed over the ocean is \qty{7}{\meter\per\second}. 
        The clouds in the planet's atmosphere consist of spherical water droplets. 
        The cloud coverage fraction is 0.5. 
        The cloud pattern is patchy, and the glint is kept cloud-free to maximize the glint signature \citep[see also Fig. 9 of][from which we took the mean signal of 300 planets with randomly generated patchy cloud patterns + 2 standard deviations, representative for cloud-free glint scenarios; the \enquote{noise} at the larger phase angles and longer wavelengths is due to the variation in the location of cloud patches]{treesandstam2019}. 
        The polarized flux is normalized to the total (unpolarized + polarized) flux (it is thus in fact the degree of polarization). 
        Note that the reference plane for the polarized flux is chosen such that only the polarized components perpendicular or parallel to the plane differ significantly from zero.
 %   and the latter
 %   is equals the planet's geometric albedo at phase angle $\alpha = 0^\circ$.
        %The cloudy scenario includes a low-altitude, Earth-like water 
        %cloud deck. 
        Below the plot, we show the phase angle ranges that cover the
        characteristic features of glories, rainbows, Rayleigh scattering, glint, and forward scattering by cloud particles (note that features partly overlap
        with each other).  
        %Throughout the paper we approximate feature sensitivity ranges as those that capture the rise and fall of peaks in polarized light for most habitable zone species in the UV, Optical, and IR (phase angles: glint $\sim\qtyrange{50}{70}{\degree}$; rainbow $\sim\SIrange{140}{160}{\degree}$; Rayleigh narrow of quadrature, and other forward and backscattering effects at the widest and narrowest phase angles).
    }
    \label{fig:bottplot}
\end{figure*}
